%\documentclass[times]{stvrauth}
\documentclass[times,doublespace]{stvrauth}%For paper submission
\def\baselinestretch{2} %for submission

\usepackage{moreverb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{rotating}
\usepackage{subfig}
\usepackage{listings}
\usepackage{amsthm}
\usepackage[linesnumbered,boxed,ruled,nofillcomment]{algorithm2e}
\usepackage{booktabs}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\lstset{frame=lines,escapeinside={(*@}{@*)},language=Java,captionpos=b,tabsize=3,numbers=left,numberstyle=\tiny,numbersep=5pt,breaklines=true,showstringspaces=false,basicstyle=\scriptsize,emph={label}}


% correct bad hyphenation here
\hyphenation{}

% Macros

\newcommand{\ie}{\textit{i.e.,} }
\newcommand{\eg}{\textit{e.g.,} }
\newcommand{\etal}{\emph{et~al.}}
\newcommand{\mukul}[1]{{\color{darkred}{\bf(**MP: #1**)}}}
\newcommand{\razieh}[1]{{\color{magenta}{\bf(**RNZ: #1**)}}}
\newcommand{\sarfraz}[1]{{\color{blue}{\bf(**SK: #1**)}}}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2010}

\definecolor{darkred}{rgb}{0.75,0,0}
\newcommand{\remark}[1]{\textcolor{darkred}{\textbf{$\{$#1$\}$}}}
\newcommand{\todo}[1]{\textbf{\color{darkred} \textsc{ToDo:} #1}}
\newcommand{\tbd}{\textbf{\color{darkred} TBD.}}
\newcommand{\tool}{\textsc{Quantum}}
\newcommand{\NumApps}{\textsc{6}}
\newcommand{\NumBugs}{\textsc{22}}
\newcommand{\NumTests}{\textsc{60}}
\newcommand{\NumAppsStudy}{\textsc{13}}
\newcommand{\NumBugsStudy}{\textsc{106}}
\newtheorem{mydef}{Definition}
\newtheorem{theorem}{Theorem}
% Test to check push

\begin{document}

\runningheads{R. Nokhbeh Zaeem \etal}{Automated Generation of Oracles for Testing Mobile Apps}

\title{Automated Generation of Oracles for Testing User-interaction Features of Mobile Apps}

\author{Razieh Nokhbeh Zaeem\affil{1}\corrauth\footnotemark[2],
Mukul R. Prasad\affil{2} and Sarfraz Khurshid\affil{1}}

\address{\affilnum{1}The University of Texas at Austin, 1 University Station C5000, Austin, TX 78712\break
\affilnum{2}Fujitsu Laboratories of America, 1240 E. Arques Ave. M/S 345, Sunnyvale, CA 94085}

\corraddr{The University of Texas at Austin, Austin, TX 78712. E-mail: nokhbeh@utexas.edu}
%\cgs{<Contract/grant sponsor name (no number)>}
\cgsn{Fujitsu Labs of America and the National Science Foundation}{SRA No. UTA12-001194 and NSF Grant Nos. CCF-0845628 and CNS-1239498.}

\begin{abstract}

As the use of mobile devices becomes increasingly ubiquitous, the need
for systematically testing applications (apps) that run on these
devices grows more and more.  However, testing mobile apps is
particularly expensive and tedious, often requiring substantial manual
effort.  While researchers have made much progress in automated
testing of mobile apps during recent years, a key problem that remains
largely untackled is the classic \emph{oracle} problem, i.e., to
determine the correctness of test executions.  This paper presents a
novel approach to automatically generate test cases, that include test oracles,
for mobile apps.
The foundation for our approach is a comprehensive study that we conducted of real defects in mobile
apps. Our key insight, from this study, is that
there is a class of features that we term \emph{user-interaction} features,
which is implicated in a significant fraction of bugs and for
which oracles can be constructed -- in an application agnostic manner --
based on our common understanding of how apps behave.  We present an extensible
framework that supports such domain specific, yet application
agnostic, test oracles, and allows generation of test sequences that
leverage these oracles.
Our tool, \tool, embodies our approach for generating test
cases that include oracles.  Experimental results using $\NumApps$ Android
apps show the effectiveness of \tool{} in finding potentially serious
bugs, while generating compact test suites for user-interaction features.

\end{abstract}

\keywords{software testing; oracles; mobile apps; Android; user-interaction features}

\maketitle
\footnotetext[2]{This author was an Intern at Fujitsu Labs of America for a part of this work.}

\setcounter{footnote}{0}
\input{introduction}
\input{study}
\input{example}
\input{framework}
\input{evaluation}
\input{relatedwork}
\input{conclusion}


\ack We thank Guowei Yang for detailed discussions and comments on this work. 
This work was funded in part by the Fujitsu Labs of America (SRA No. UTA12-001194) and the National Science Foundation (NSF Grant Nos. CCF-0845628 and CNS-1239498).

\bibliographystyle{wileyj}
\bibliography{paper}

\end{document}


